---
title: '**Hollywood Closet Project:** *Exploratory Data Analysis*'
author: "Samuel Campione"
output: 
  github_document:
    toc: yes
    toc_depth: 2
always_allow_html: true
---

<br>

------------------------------------------------------------------------

## Overview

##### [*I worked on collecting this dataset as an RA in my undergrad. I decided to do a more in-depth analysis to see what insights may be gained about the data.*]{style="color: dimgray;"}

<br>

##### [*Because the sample was non-randomly selected and was not designed to comply with the theoretical assumptions of statistical tests, I decided to not include inferential procedures for lack of external validity. However, the descriptive statistics and visualizations provide fascinating insight into the sample. Further, these analyses provide an idea of how the population may look.*]{style="color: dimgray;"} 

<br>

##### [*Future endeavors should focus on further collection of data to provide a more representative sample to gain firmer insight.*]{style="color: dimgray;"}

## [Research Questions]{style="color: steelblue;"}

-   What do the variables in this data set look like with descriptive statistics and data visualization?
-   How has the age of coming out changed over time?
-   Are people coming out at a younger age in more recent years?
-   How do all of these look across race, gender, and sexuality?

------------------------------------------------------------------------

## [1]{style="color: steelblue;"} [Load the data set]{style="color: black;"}

------------------------------------------------------------------------

```{r message=FALSE, warning=FALSE, class.source = "fold-show"}
options(warn = -1) # Turn off warning messages

# Load required libraries
suppressMessages(library(tidyverse))
suppressMessages(library(wesanderson))
suppressMessages(library(forcats))
suppressMessages(library(knitr))
suppressMessages(library(kableExtra))
suppressMessages(library(ggrepel))
suppressMessages(library(patchwork))
```

<br>

### [1.1]{style="color: lightgray;"} Read in the file

```{r class.source = "fold-show"}
data <- read.csv("HCP_data.csv", na.strings = c("","NA"))
```

<br>

### [1.2]{style="color: lightgray;"} Preview the `data`

```{r class.source = "fold-show", fig.align='center'}
head(data)
```

<br>

------------------------------------------------------------------------

## [2]{style="color: steelblue;"} [Data Wrangling and Cleaning]{style="color: black;"}

------------------------------------------------------------------------

<br>

### [2.1]{style="color: lightgrey;"} Relabel columns

```{r class.source = "fold-show"}
colnames(data) = c("id", "first_name", "last_name", "race", "birth_year", "age", 
                  "coming_out_year", "medium", "initiation", "disclosure", "sexuality", 
                  "closeted", "gender", "coming_out_nature_2", "sexuality_2")
```

<br>

### [2.2]{style="color: lightgrey;"} Merge `first_name` and `last_name`

```{r class.source = "fold-show"}
data <- data %>%
  unite("name", first_name:last_name, sep=" ")
```

<br>

### [2.3]{style="color: lightgrey;"} Convert variables to correct data types

```{r class.source = "fold-show"}
# All character variables to factors
data <- data %>%
  mutate_if(sapply(data, is.character), as.factor)
```

<br>

### [2.4]{style="color: lightgrey;"} Create variable `coming_out_2` to easily explore subset

```{r class.source = "fold-show"}
data<- data %>% 
  mutate(coming_out_2 = ifelse(is.na(coming_out_nature_2), 0, 1) ,.after = gender)
```

<br>

------------------------------------------------------------------------

## [3]{style="color: steelblue;"} [Data Visualization and Summary]{style="color: black;"}

------------------------------------------------------------------------

<br>

## [3.1]{style="color: lightgrey;"} [Univariate Analysis]{style="color: dimgrey;"}

<br>

------------------------------------------------------------------------

### [3.1.1]{style="color: lightgrey;"} [Race]{style="color: steelblue;"}

```{r echo=FALSE, warning=TRUE, fig.align='center'}
pct_format <- scales::percent_format(accuracy = .1) #Used in the future bar plots

data %>%
  filter(race != "Unknown") %>%
  ggplot(aes(x = fct_infreq(race), fill = fct_infreq(race))) +
  geom_bar() +
  guides(fill = "none") +
  geom_text(
    aes(label = sprintf(
      "%d (%s)", ..count.., pct_format(..count.. / sum(..count..))
    )),
    stat = "count",
    nudge_y = 5,
    colour = "black",
    size = 4,
    fontface = "bold"
  ) +
  labs(title = "Figure 1.1", x = "", y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(size = 12, vjust = -1)) +
  scale_fill_manual(values = wes_palette("Moonrise3", 5, type = "continuous"))
```

```{r echo=FALSE, fig.align='center'}
data %>%
  filter(!is.na(race)) %>%
  group_by(race) %>%
  rename(Race = race) %>%
  summarise(Frequency = n()) %>%
  mutate("Relative Frequency" = round(Frequency / sum(Frequency), 3)) %>%
  kable(caption = "TABLE 1.1: Race",
        table.attr = "style='width:65%;'") %>%
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 18) %>%
  row_spec(0, bold = TRUE)
```

<br>

#### [Any missing values?]{style="color: grey;"}

```{r echo=FALSE}
# Create function to calculate return # of NAs in a variable
NA_calc <- function(x) {
  a <- sum(is.na(x))
  print(paste("Missing Values (NAs):" , a))
}
NA_calc(data$race)
```

<br>

------------------------------------------------------------------------

### [3.1.2]{style="color: lightgrey;"} [Gender]{style="color: steelblue;"}

```{r echo=FALSE, fig.align='center'}
data %>%
  filter(!is.na(gender)) %>%
  ggplot(aes(x = fct_infreq(gender), fill = fct_infreq(gender))) +
  geom_bar() +
  guides(fill = "none") +
  geom_text(
    aes(label = sprintf(
      "%d (%s)", ..count.., pct_format(..count.. / sum(..count..))
    )),
    stat = "count",
    nudge_y = 5,
    colour = "black",
    size = 3.5,
    fontface = "bold"
  ) +
  labs(title = "Figure 1.2", x = "", y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(
    size = 11,
    angle = 25,
    hjust = 1
  )) +
  scale_fill_manual(values = wes_palette("Moonrise3", 10, type = "continuous"))
```

```{r fig.align='center', echo=FALSE}
data %>%
  filter(!is.na(gender)) %>%
  group_by(gender) %>%
  rename(Gender = gender) %>%
  summarise(Frequency = n()) %>%
  mutate("Relative Frequency" = round(Frequency / sum(Frequency), 3)) %>%
  kable(caption = "TABLE 1.2: Gender",
        table.attr = "style='width:65%;'") %>%
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 18) %>%
  row_spec(0, bold = TRUE)
```

<br>

#### [Any missing values?]{style="color: grey;"}

```{r fig.align='center', echo=FALSE}
NA_calc(data$gender)
```

<br>

------------------------------------------------------------------------

### [3.1.3]{style="color: lightgrey;"} [Sexuality]{style="color: steelblue;"}

```{r message=FALSE, warning=FALSE, fig.align='center', echo=FALSE}
#The value "Unspecified non heterosexual" fits poorly, so I have revalued it to "Non heterosexual".
data %>%
  filter(!is.na(sexuality)) %>%
  mutate(sexuality = fct_recode(sexuality, "Non heterosexual" = "Unspecified non heterosexual")) %>%
  ggplot(aes(x = fct_infreq(sexuality), fill = fct_infreq(sexuality))) +
  geom_bar() +
  guides(fill = "none") +
  geom_text(
    aes(label = sprintf(
      "%d (%s)", ..count.., pct_format(..count.. / sum(..count..))
    )),
    stat = "count",
    nudge_y = 5,
    colour = "black",
    size = 3.5,
    fontface = "bold"
  ) +
  labs(title = "Figure 1.3", x = "", y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(
    size = 12,
    angle = 35,
    hjust = 1.0
  )) +
  scale_fill_manual(values = wes_palette("Moonrise3", 9, type = "continuous"))
```

```{r fig.align='center', echo=FALSE}
data %>%
  filter(!is.na(sexuality)) %>%
  group_by(sexuality) %>%
  mutate(sexuality = fct_recode(sexuality, "Non heterosexual" = "Unspecified non heterosexual")) %>%
  rename(Sexuality = sexuality) %>%
  summarise(Frequency = n()) %>%
  mutate("Relative Frequency" = round(Frequency / sum(Frequency), 3)) %>%
  kable(caption = "TABLE 1.3: Sexuality",
        table.attr = "style='width:60%;'") %>%
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 18) %>%
  row_spec(0, bold = TRUE)
```

<br>

#### [Any missing values?]{style="color: grey;"}

```{r echo=FALSE, fig.align='center'}
NA_calc(data$sexuality)
```

<br>

------------------------------------------------------------------------

### [3.1.2]{style="color: lightgrey;"} [In the closet?]{style="color: steelblue;"}

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
data %>%
  filter(!is.na(closeted)) %>%
  ggplot(aes(x = closeted, fill = closeted)) +
  geom_bar() +
  guides(fill = "none") +
  geom_text(
    aes(label = sprintf(
      "%d (%s)", ..count.., pct_format(..count.. / sum(..count..))
    )),
    stat = "count",
    nudge_y = 5,
    colour = "black",
    size = 3.5,
    fontface = "bold"
  ) +
  labs(title = "Figure 1.4", x = "", y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(size=12, angle = 35, hjust = 1)) +
  scale_fill_manual(values = c("#85D4E3","LightBlue", "Linen", "#F4B5BD", "MistyRose"))
```

```{r echo=FALSE, fig.align='center'}
data %>%
  filter(!is.na(closeted)) %>%
  group_by(closeted) %>%
  rename("Closeted?" = closeted) %>%
  summarise(Frequency = n()) %>%
  mutate("Relative Frequency" = round(Frequency/sum(Frequency), 3)) %>%
  kable(caption = "TABLE 1.4: Closeted before coming out", 
        table.attr = "style='width:65%;'") %>% 
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 18) %>%
  row_spec(0,bold=TRUE)
```

<br>

#### [Any missing values?]{style="color: grey;"}

```{r echo=FALSE, fig.align='center'}
NA_calc(data$closeted)
```

<br>

------------------------------------------------------------------------

### [3.1.5]{style="color: lightgrey;"} [Coming Out Medium]{style="color: steelblue;"}

```{r echo=FALSE, fig.align='center'}
data %>%
  filter(!is.na(medium)) %>%
  ggplot(aes(x = fct_infreq(medium), fill = fct_infreq(medium))) +
  geom_bar() +
  guides(fill = "none") +
  geom_text(
    aes(label = sprintf(
      "%d (%s)", ..count.., pct_format(..count.. / sum(..count..))
    )),
    stat = "count",
    nudge_y = 5,
    colour = "black",
    size = 3.5,
    fontface = "bold"
  ) +
  labs(title = "Figure 1.5", x = "", y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(size=11, angle=35, hjust = 1)) +
  scale_fill_manual(values = wes_palette("Moonrise3", 6, type = "continuous"))
```

```{r echo=FALSE, fig.align='center'}
data %>%
  group_by(medium) %>%
  filter(!is.na(medium)) %>%
  rename(Medium = medium) %>%
  summarise(Frequency = n()) %>%
  mutate("Relative Frequency" = round(Frequency/sum(Frequency), 3)) %>%
  kable(caption = "TABLE 1.5: Medium of coming out",
        table.attr = "style='width:65%;'") %>% 
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 18) %>%
  row_spec(0,bold=TRUE)
```

<br>

#### [Any missing values?]{style="color: grey;"}

```{r echo=FALSE, fig.align='center'}
NA_calc(data$medium)
```

<br>

------------------------------------------------------------------------

### [3.1.6]{style="color: lightgrey;"} [Who Initiated Coming Out?]{style="color: steelblue;"}

```{r echo=FALSE, fig.width= 4, fig.align='center'}
data %>%
  filter(!is.na(initiation)) %>%
  ggplot(aes(x = fct_infreq(initiation), fill = fct_infreq(initiation))) +
  geom_bar() +
  guides(fill = "none") +
  geom_text(
    aes(label = sprintf(
      "%d (%s)", ..count.., pct_format(..count.. / sum(..count..))
    )),
    stat = "count",
    nudge_y = 5,
    colour = "black",
    size = 4,
    fontface = "bold"
  ) +
  labs(title = "Figure 1.6: Initiation", x = "", y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(size=12)) +
  scale_fill_manual(values = wes_palette("Moonrise3", 2, type = "continuous"))
```

```{r echo=FALSE, fig.align='center'}
data %>%
  group_by(initiation) %>%
  filter(!is.na(initiation)) %>%
  rename(Initiation = initiation) %>%
  summarise(Frequency = n()) %>%
  mutate("Relative Frequency" = round(Frequency/sum(Frequency), 3)) %>%
  kable(caption = "TABLE 1.6: Who initiated coming out",
        table.attr = "style='width:65%;'") %>% 
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 18) %>%
  row_spec(0,bold=TRUE)
```

<br>

#### [Any missing values?]{style="color: grey;"}

```{r echo=FALSE, fig.align='center'}
NA_calc(data$initiation)
```

<br>

------------------------------------------------------------------------

### [3.1.7]{style="color: lightgrey;"} [Who Disclosed?]{style="color: steelblue;"}

```{r echo=FALSE, fig.width= 4, fig.align='center'}
data %>%
  filter(!is.na(disclosure)) %>%
  ggplot(aes(x = fct_infreq(disclosure), fill = fct_infreq(disclosure))) +
  geom_bar() +
  guides(fill = "none") +
  geom_text(
    aes(label = sprintf(
      "%d (%s)", ..count.., pct_format(..count.. / sum(..count..))
    )),
    stat = "count",
    nudge_y = 5,
    colour = "black",
    size = 4,
    fontface = "bold"
  ) +
  labs(title = "Figure 1.7: Disclosure", x = "", y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(size=12)) +
  scale_fill_manual(values = wes_palette("Moonrise3", 2, type = "continuous"))
```

```{r echo=FALSE, fig.align='center'}
data %>%
  group_by(disclosure) %>%
  filter(!is.na(disclosure)) %>%
  rename(Disclosure = disclosure) %>%
  summarise(Frequency = n()) %>%
  mutate("Relative Frequency" = round(Frequency/sum(Frequency), 3)) %>%
  kable(caption = "TABLE 1.7: Who disclosed",  table.attr = "style='width:65%;'") %>% 
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 18) %>%
  row_spec(0,bold=TRUE)
```

<br>

#### [Any missing values?]{style="color: grey;"}

```{r echo=FALSE, fig.align='center'}
NA_calc(data$disclosure)
```

<br>

------------------------------------------------------------------------

### [3.1.8]{style="color: lightgrey;"} [Had Second Coming Out?]{style="color: steelblue;"}

```{r echo=FALSE, fig.width= 4, fig.align='center'}
data %>%
  filter(!is.na(coming_out_2)) %>%
  mutate(coming_out_2 = as.factor(coming_out_2)) %>%
  mutate(coming_out_2 = if_else(coming_out_2 == "1", "Yes", "No")) %>%
  ggplot(aes(x = fct_infreq(coming_out_2), fill = fct_infreq(coming_out_2))) +
  geom_bar() +
  guides(fill = "none") +
  geom_text(
    aes(label = sprintf(
      "%d (%s)", ..count.., pct_format(..count.. / sum(..count..))
    )),
    stat = "count",
    nudge_y = 5,
    colour = "black",
    size = 4.5,
    fontface = "bold"
  ) +
  labs(title = "Figure 1.8", x = "", y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(size=12)) +
  scale_fill_manual(values = wes_palette("Moonrise3", 2, type = "continuous"))
```

```{r echo=FALSE, fig.align='center'}
data %>%
  group_by(coming_out_2) %>%
  filter(!is.na(coming_out_2)) %>%
  mutate(coming_out_2 = as.factor(coming_out_2)) %>%
  mutate(coming_out_2 = if_else(coming_out_2 == "1", "Yes", "No")) %>%
  rename("Had 2nd Coming Out" = coming_out_2) %>%
  summarise(Frequency = n()) %>%
  mutate("Relative Frequency" = round(Frequency/sum(Frequency), 2)) %>%
  kable(caption = "TABLE 1.8: Second coming out events", table.attr = "style='width:65%;'") %>%
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 18) %>%
  row_spec(0,bold=TRUE)
```

<br>

#### [Any missing values?]{style="color: grey;"}

```{r echo=FALSE, fig.align='center'}
NA_calc(data$coming_out_2)
```

<br>

------------------------------------------------------------------------

### [3.1.9]{style="color: lightgrey;"} [Second Coming Out Nature]{style="color: steelblue;"}

```{r echo=FALSE, fig.width= 4, fig.align='center'}
data %>%
  filter(coming_out_2 == 1, 
         !is.na(coming_out_nature_2)) %>%
  ggplot(aes(x = fct_infreq(coming_out_nature_2), fill = fct_infreq(coming_out_nature_2))) +
  geom_bar() +
  guides(fill = "none") +
  geom_text(
    aes(label = sprintf(
      "%d (%s)", ..count.., pct_format(..count.. / sum(..count..))
    )),
    stat = "count",
    nudge_y = 1,
    colour = "black",
    size = 4.5,
    fontface = "bold"
  ) +
  labs(title = "Figure 1.9", x = "", y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(size=12)) +
  scale_fill_manual(values = wes_palette("Moonrise3", 2, type = "continuous"))
```

```{r echo=FALSE, fig.align='center'}
data %>%
  group_by(coming_out_nature_2) %>%
  filter(coming_out_2 == 1,
         !is.na(coming_out_nature_2)) %>%
  rename("Nature" = coming_out_nature_2) %>%
  summarise(Frequency = n()) %>%
  mutate("Relative Frequency" = round(Frequency/sum(Frequency), 2)) %>%
  kable(caption = "TABLE 1.9: Nature of second coming out", table.attr = "style='width:65%;'") %>%
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 18) %>%
  row_spec(0,bold=TRUE)
```

<br>

#### [Any missing values?]{style="color: grey;"}

```{r echo=FALSE, fig.align='center'}
subset <- data %>%
  filter(coming_out_2 == 1)
NA_calc(subset$coming_out_nature_2)
```

<br>

------------------------------------------------------------------------

### [3.1.10]{style="color: lightgrey;"} [Second Coming Out Sexuality]{style="color: steelblue;"}

```{r echo=FALSE, fig.align='center'}
data %>%
  filter(coming_out_2 == 1, 
         !is.na(sexuality_2)) %>%
  mutate(sexuality_2 = fct_recode(sexuality_2,"Non heterosexual"= "Unspecified non heterosexual")) %>%
  ggplot(aes(x = fct_infreq(sexuality_2), fill = fct_infreq(sexuality_2))) +
  geom_bar() +
  guides(fill = "none") +
  geom_text(
    aes(label = sprintf(
      "%d (%s)", ..count.., pct_format(..count.. / sum(..count..))
    )),
    stat = "count",
    nudge_y = .65,
    colour = "black",
    size = 3.45,
    fontface = "bold"
  ) +
  labs(title = "Figure 1.10", x = "", y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(size=12, angle = 45, hjust = 1)) +
  scale_fill_manual(values = wes_palette("Moonrise3", 10, type = "continuous"))
```

```{r echo=FALSE, fig.align='center'}
data %>%
  mutate(sexuality_2 = fct_recode(sexuality_2, "Non heterosexual"= "Unspecified non heterosexual",
                                  "Unspecified" = "Unspecified ")) %>%
  group_by(sexuality_2) %>%
  filter(coming_out_2 == 1,
         !is.na(sexuality_2)) %>%
  rename("Sexuality" = sexuality_2) %>%
  summarise(Frequency = n()) %>%
  mutate("Relative Frequency" = round(Frequency/sum(Frequency), 2)) %>%
  kable(caption = "TABLE 1.10: Sexuality at second coming out", table.attr = "style='width:75%;'") %>%
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 18) %>%
  row_spec(0,bold=TRUE)
```

<br>

#### [Any missing values?]{style="color: grey;"}

```{r echo=FALSE, fig.align='center'}
NA_calc(subset$sexuality_2)
```

<br>

### [3.1.11]{style="color: lightgrey;"} [Current Age]{style="color: steelblue;"}

<br>

#### Current ages in 2022 based on birth year. For simplicity, I applied a filter to include only those under 100 years old

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
p1 <- data %>%
  filter(!is.na(birth_year)) %>%
  mutate(current_age = 2022 - birth_year) %>%
  filter(current_age < 100) %>%
  ggplot(aes(x = current_age)) +
  geom_histogram(
    fill = "#85D4E3",
    colour = 1,
    binwidth = 5,
    size = .25
  ) +
  guides(fill = "none", colour = "none") +
  labs(title = "Figure 1.11",
       x = "Age",
       y = "Count") +
  coord_cartesian(xlim = c(10, 100), ylim = c(0, 40)) +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 20,
                                  face = "bold"))

p2 <- data %>%
  filter(!is.na(birth_year)) %>%
  mutate(current_age = 2022 - birth_year) %>%
  filter(current_age < 100) %>%
  ggplot(aes(x = current_age, y = ..density..)) +
  geom_density(lwd = .75, fill = "lightgray") +
  guides(fill = "none", colour = "none") +
  labs(x = "Age",
       y = "Density") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 20,
                                  face = "bold")) +
  xlim(0, 100) +
  geom_vline(
    aes(xintercept = median(current_age)),
    color = "red",
    size = 0.75,
    linetype = "longdash"
  ) +
  geom_text(aes(
    median(current_age),
    y = 0.03,
    label = paste("median =", median(current_age)),
    hjust = -.3,
  ),
  size = 5.9,
  face = "plain")

p1 + p2
```
<br>
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height= 2.5, fig.align='center'}
is.outlier <- function(x) {
  return(x  < quantile(x, 0.25) - 1.5 * IQR(x) |
           x > quantile(x, 0.75) + 1.5 * IQR(x))
}

data %>%
  filter(!is.na(birth_year)) %>%
  mutate(current_age = 2022 - birth_year) %>%
  mutate(Outlier = ifelse(is.outlier(current_age), current_age, "")) %>%
  ggplot(aes(x = current_age, y = "")) +
  geom_boxplot(
    fill = "lightgray",
    outlier.shape = 5,
    outlier.color = "red",
    outlier.size = 4
  ) +
  labs(title = "Boxplot of Current Age",
       x = "Age",
       y = "") +
  theme_classic() +
  theme(axis.ticks.y = element_blank(),
        axis.text.y  = element_blank()) +
  theme(plot.title = element_text(size = 14,
                                  face = "bold")) +
  geom_text_repel(aes(label = ifelse(duplicated(Outlier), "", Outlier))) +
  annotate("text", x = 41 + 5, y = 1.5, label = paste("median = 41"), fontface = 2)
```
<br>
```{r echo=FALSE, fig.align='center'}
data %>%
  filter(!is.na(birth_year)) %>%
  mutate(current_age = 2022 - birth_year) %>%
  summarise(Mean =  round(mean(current_age),1),
            SD =  round(sd(current_age),1),
            Median = median(current_age),
            Min = min(current_age),
            Max = max(current_age),
            NAs = sum(is.na(age))
            ) %>%
  kable(caption = "TABLE 1.11: Summary of Current Ages", table.attr = "style='width:40%;'") %>% 
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 20) %>%
  row_spec(0,bold=TRUE)
```

<br>

------------------------------------------------------------------------

### [3.1.12]{style="color: lightgrey;"} [Coming Out Year]{style="color: steelblue;"}

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
p1 <- data %>%
  filter(!is.na(coming_out_year), 
         coming_out_year > 1940) %>%
  ggplot(aes(x = coming_out_year)) +
  geom_histogram(
    fill = "#85D4E3",
    colour = 1,
    binwidth = 2,
    size = .25
  ) +
  guides(fill = "none", colour = "none") +
  labs(title = "Figure 1.12",
       x = "Year",
       y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 20,
                                  face = "bold"))

p2 <- data %>%
  filter(!is.na(coming_out_year),
         coming_out_year > 1940) %>%
  ggplot(aes(x = coming_out_year, y = ..density..)) +
  geom_density(lwd = .75, fill = "lightgray") +
  guides(fill = "none", colour = "none") +
  labs(x = "Year",
       y = "Density") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 20,
                                  face = "bold")) +
  geom_vline(
    aes(xintercept = median(coming_out_year)),
    color = "red",
    size = 0.75,
    linetype = "longdash"
  ) +
  geom_text(aes(
    median(coming_out_year),
    y = 0.05,
    label = paste("median =", median(coming_out_year)),
    hjust = 1.2
  ),
  size = 5.9,
  face = "plain")

p1 + p2
```
<br>

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height= 2.5, fig.align='center'}
is.outlier <- function(x) {
  return(x  < quantile(x, 0.25) - 1.5 * IQR(x) |
           x > quantile(x, 0.75) + 1.5 * IQR(x))
}

data %>%
  filter(!is.na(coming_out_year)) %>%
  mutate(Outlier = ifelse(is.outlier(coming_out_year), coming_out_year, "")) %>%
  ggplot(aes(x = coming_out_year, y = "")) +
  geom_boxplot(
    fill = "lightgray",
    outlier.shape = 5,
    outlier.color = "red",
    outlier.size = 4
  ) +
  labs(title = "Boxplot of Coming Out Year",
       x = "Year",
       y = "") +
  theme_classic() +
  theme(axis.ticks.y = element_blank(),
        axis.text.y  = element_blank()) +
  theme(plot.title = element_text(size = 14,
                                  face = "bold")) +
  geom_text_repel(aes(label = ifelse(duplicated(Outlier), "", Outlier))) +
  annotate("text", x = median(data$coming_out_year, na.rm = T) -2, y = 1.5, label = paste("median = ", median(data$coming_out_year, na.rm = T)), fontface = 2)
```
<br>
```{r echo=FALSE, fig.align='center'}
data %>%
  filter(!is.na(coming_out_year)) %>%
  summarise(Mean =  round(mean(coming_out_year)),
            SD =  round(sd(coming_out_year)),
            Median = median(coming_out_year),
            Min = min(coming_out_year),
            Max = max(coming_out_year),
            NAs = sum(is.na(age))
            ) %>%
  kable(caption = "TABLE 1.12: Summary of Coming Out Years", table.attr = "style='width:45%;'") %>% 
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 20) %>%
  row_spec(0,bold=TRUE)
```

<br>

------------------------------------------------------------------------

### [3.1.13]{style="color: lightgrey;"} [Age at Coming Out]{style="color: steelblue;"}

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
p1 <- data %>% 
  filter(!is.na(age)) %>%
  ggplot(aes(x = age)) +
  geom_histogram(
    fill = "#85D4E3",
    colour = 1,
    binwidth = 2,
    size = .25
  ) +
  guides(fill = "none", colour = "none") +
  labs(title = "Figure 1.13",
       x = "Age",
       y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 20,
                                  face = "bold"))

p2 <- data %>%
  filter(!is.na(age)) %>%
  ggplot(aes(x = age, y = ..density..)) +
  geom_density(lwd = .75, fill = "lightgray") +
  guides(fill = "none", colour = "none") +
  labs(x = "Age",
       y = "Density") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 20,
                                  face = "bold")) +
  geom_vline(
    aes(xintercept = median(age)),
    color = "red",
    size = 0.75,
    linetype = "longdash"
  ) +
  annotate("text",
           x = median(data$age, na.rm = T),
           y = 0.035,
           label = paste("median =", median(data$age, na.rm = T)),
           hjust = -.35,
           fontface = 2,
           size = 5.9)

p1 + p2
```
<br>

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height= 2.5, fig.align='center'}
is.outlier <- function(x) {
  return(x  < quantile(x, 0.25) - 1.5 * IQR(x) |
           x > quantile(x, 0.75) + 1.5 * IQR(x))
}

data %>%
  filter(!is.na(age)) %>%
  mutate(Outlier = ifelse(is.outlier(age), age, "")) %>%
  ggplot(aes(x = age, y = "")) +
  geom_boxplot(
    fill = "lightgray",
    outlier.shape = 5,
    outlier.color = "red",
    outlier.size = 4
  ) +
  labs(title = "Boxplot of Coming Out Age",
       x = "Age",
       y = "") +
  theme_classic() +
  theme(axis.ticks.y = element_blank(),
        axis.text.y  = element_blank()) +
  theme(plot.title = element_text(size = 14,
                                  face = "bold")) +
  geom_text_repel(aes(label = ifelse(duplicated(Outlier), "", Outlier))) +
  annotate("text", x = median(data$age, na.rm = T) + 10, y = 1.5, label = paste("median = ", median(data$age, na.rm = T)), fontface = 2)
```

```{r echo=FALSE, fig.align='center'}
data %>%
  filter(!is.na(age)) %>%
  summarise(Mean =  round(mean(age),1),
            SD =  round(sd(age),1),
            Median = median(age),
            Min = min(age),
            Max = max(age),
            NAs = sum(is.na(age))
            ) %>%
  kable(caption = "TABLE 1.13: Summary of Coming Out Age", table.attr = "style='width:40%;'") %>% 
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 20) %>%
  row_spec(0,bold=TRUE)
```

<br>

------------------------------------------------------------------------

## [3.2]{style="color: lightgrey;"} [Multivariate Analysis]{style="color: dimgrey;"}

<br>

------------------------------------------------------------------------

### [3.2.1]{style="color: lightgrey;"} [Coming Out Age & Birth Year]{style="color: steelblue"}

#### [Are younger generations coming out at a younger age?]{style="color: grey;"}

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
data %>%
  mutate(decade = cut(birth_year, breaks = c(0, 1946, 1965, 1977, 1995, Inf),
    labels = c("Pre-Boomer", "Boomer", "Gen X", "Millenial", "Gen Z")), include.lowest = TRUE, exclude=NULL) %>%
  group_by(decade) %>%
  filter(!is.na(age)) %>%
  ggplot(aes(x = birth_year, y = age, color = decade)) +
  geom_point(aes(color = decade, alpha = 0.5)) +
  geom_smooth(formula = y ~ x, method=lm, se=FALSE) + 
  labs(title = "Figure 2.1a",
       subtitle = "Coming Out Age and Generation",
       x = "Year",
       y = "Coming Out Age") +
  guides(color=guide_legend(title="Generation"),
         alpha="none") +
  theme_classic() + 
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(size=12)) +
  scale_color_manual(values =wes_palette("Moonrise3", 5))
```

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
data %>%
  mutate(decade = cut(birth_year, breaks = c(0, 1946, 1965, 1977, 1995, Inf),
    labels = c("Pre-Boomer", "Boomer", "Gen X", "Millenial", "Gen Z")), include.lowest = TRUE, exclude=NULL) %>%
  group_by(decade) %>%
  filter(!is.na(age)) %>%
  ggplot(aes(x = decade, y = age, fill = decade)) +
  geom_boxplot() +
  labs(title = "Figure 2.1b",
       subtitle = "Coming Out Age and Generation",
       x = "",
       y = "Coming Out Age") +
  guides(fill=guide_legend(title="Generation"),
         alpha="none") +
  theme_classic() + 
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  scale_fill_manual(values =wes_palette("Moonrise3", 5)) +
  theme(axis.text.x = element_text(size=12)) +
  geom_smooth(formula = y ~ x, method = "lm", se=TRUE, aes(group=1), color = "dimgray", linetype="dashed", size = .5)
```

<br>

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
data %>% 
  mutate(decade = cut(birth_year, breaks = c(0, 1946, 1965, 1977, 1995, Inf),
    labels = c("Pre-Boomer", "Boomer", "Gen X", "Millenial", "Gen Z")), include.lowest = TRUE, exclude=NULL) %>%
  group_by(decade) %>%
  filter(!is.na(age)) %>%
  summarize(count = n(),
            mean = round(mean(age), 2)) %>%
  kable(caption = "TABLE 2.1: Birth Decade and Coming Out Age", table.attr = "style='width:50%;'", col.names = c("Decade","Count","Mean Coming Out Age")) %>% 
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 20) %>%
  row_spec(0,bold=TRUE) 
```

<br>

------------------------------------------------------------------------

### [3.2.2.]{style="color: lightgrey;"} [Coming Out Age & Race]{style="color: steelblue"}

#### [What does coming out age look across race?]{style="color: grey;"}

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
data %>%
  group_by(race) %>%
  filter(race != "Unknown") %>%
  ggplot(aes(x = race, y = age, fill = race)) +
  geom_boxplot() +
  geom_jitter(shape = 16,
      color = "steelblue",
      position = position_jitter(0.21)) +
  theme_classic() +
  scale_fill_manual(values = wes_palette("Moonrise3", 5, type = "continuous")) +
  labs(title = "Figure 2.2",
       subtitle = "Coming Out Age by Race",
       x = "",
       y = "Coming Out Age") + 
  theme(axis.text.x = element_text(size=12)) +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold"))
```

<br>

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
data %>%
  filter(!is.na(age)) %>%
  group_by(race) %>%
  summarize( n(),
            round(mean(age),2),
            round(median(age),2),
            round(min(age),2),
            round(max(age),2)) %>%
  kable(caption = "TABLE 2.2: Race and Coming Out Age", table.attr = "style='width:50%;'", col.names = c("Race","Count","Mean", "Median", "Min", "Max")) %>% 
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 20) %>%
  row_spec(0,bold=TRUE) 
```

<br>

------------------------------------------------------------------------

### [3.2.3]{style="color: lightgrey;"} [Coming Out Age & Gender]{style="color: steelblue"}

#### [What does coming out age look across gender?]{style="color: grey;"}

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
data %>%
  group_by(gender) %>%
  filter(!is.na(gender)) %>%
  # Collapse the levels of Queer, Unspecified Queer, Genderqueer to just Queer
  mutate(gender = fct_collapse(gender, Queer = c("Queer","Genderqueer", "Unspecified queer"))) %>% 
  ggplot(aes(x = gender, y = age, fill = gender)) +
  geom_boxplot() +
  geom_jitter(shape = 16,
      color = "steelblue",
      position = position_jitter(0.21)) +
  theme_classic() +
  scale_fill_manual(values = wes_palette("Moonrise3", 7, type = "continuous")) +
  labs(title = "Figure 2.3",
       subtitle = "Coming Out Age by Gender",
       x = "",
       y = "Coming Out Age") + 
  theme(axis.text.x = element_text(size=12, angle = 45, hjust = 1)) +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold"))
```

<br>

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
data %>%
  filter(!is.na(age),
         !is.na(gender)) %>%
  group_by(gender) %>%
  # Collapse the levels of Queer, Unspecified Queer, Genderqueer to just Queer
  mutate(gender = fct_collapse(gender, Queer = c("Queer","Genderqueer", "Unspecified queer"))) %>% 
  summarize( n(),
            round(mean(age),2),
            round(median(age),2),
            round(min(age),2),
            round(max(age),2)) %>%
  kable(caption = "TABLE 2.3: Gender and Coming Out Age", table.attr = "style='width:60%;'", col.names = c("Gender","Count","Mean", "Median", "Min", "Max")) %>% 
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 20) %>%
  row_spec(0,bold=TRUE) 
```

<br>

------------------------------------------------------------------------

### [3.2.4]{style="color: lightgrey;"} [Coming Out Age & Sexuality]{style="color: steelblue"}

#### [What does coming out age look across sexuality?]{style="color: grey;"}

<br>

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
data %>%
  group_by(sexuality) %>%
  filter(!is.na(sexuality),
         age < 100) %>%
  # Recode "Unspecified non heterosexual" to shorten
  mutate(sexuality = fct_recode(sexuality, "Non heterosexual" = "Unspecified non heterosexual")) %>%
  mutate(sexuality = fct_collapse(sexuality, Other = c("Pansexual","Sexually fluid"))) %>% 
  ggplot(aes(x = sexuality, y = age, fill = sexuality)) +
  geom_boxplot() +
  geom_jitter(shape = 16,
      color = "steelblue",
      position = position_jitter(0.21)) +
  theme_classic() +
  scale_fill_manual(values = wes_palette("Moonrise3", 8, type = "continuous")) +
  labs(title = "Figure 2.4",
       subtitle = "Coming Out Age by Sexuality",
       x = "",
       y = "Coming Out Age") + 
  theme(axis.text.x = element_text(size=12, angle = 45, hjust = 1)) +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold"))
```

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
data %>%
  filter(!is.na(age),
         !is.na(sexuality)) %>%
  group_by(sexuality) %>%
  # Recode "Unspecified non heterosexual" to shorten
  mutate(sexuality = fct_recode(sexuality, "Non heterosexual" = "Unspecified non heterosexual")) %>%
  summarize( n(),
            round(mean(age),2),
            round(median(age),2),
            round(min(age),2),
            round(max(age),2)) %>%
  kable(caption = "TABLE 2.4: Sexuality and Coming Out Age", table.attr = "style='width:60%;'", col.names = c("Sexuality","Count","Mean", "Median", "Min", "Max")) %>% 
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 20) %>%
  row_spec(0,bold=TRUE) 
```

<br>

::: {.tocify-extend-page data-unique="tocify-extend-page" style="height: 0;"}
:::