---
title: '**Hollywood Closet Project:** *Exploratory Data Analysis*'
author: "Samuel Campione"
output:
  html_document:
    toc: yes
    df_print: paged
    code_folding: hide
---

<br>

- What do the variables in this data set look like with descriptive statistics and data visualization?
- Are people coming out at a younger age in more recent years?
- Are less people closeted now? And are less people outed by someone else?
- How has the age of coming out changed over time? 
- How do all of these look across race, gender, and sexuality?

------------------------------------------------------------------------

## [1]{style="color: steelblue;"} Load the data set

------------------------------------------------------------------------

```{r include=FALSE}
setwd( "/Users/sam/SamuelCampione/HCP")
```

```{r message=FALSE, warning=FALSE, class.source = "fold-show"}
# Load required libraries
library(tidyverse)
library(wesanderson)
library(forcats)
library(knitr)
library(kableExtra)
library(ggrepel)
library(patchwork)
```

<br>

### [1.1]{style="color: lightgray;"} Read in the file

```{r class.source = "fold-show"}
data <- read.csv("HCP_data.csv", na.strings = c("","NA"))
```

<br>

### [1.2]{style="color: lightgray;"} Preview the `data`

```{r class.source = "fold-show", fig.align='center'}
head(data)
```

<br>

------------------------------------------------------------------------

## [1]{style="color: steelblue;"} Data Wrangling and Cleaning

------------------------------------------------------------------------

<br>

### [2.1]{style="color: lightgrey;"} Relabel columns

```{r class.source = "fold-show"}
colnames(data) = c("id", "first_name", "last_name", "race", "birth_year", "age", 
                  "coming_out_year", "medium", "initiation", "disclosure", "sexuality", 
                  "closeted", "gender", "coming_out_nature_2", "sexuality_2")
```

<br>

### [2.2]{style="color: lightgrey;"} Merge `first_name` and `last_name`

```{r class.source = "fold-show"}
data <- data %>%
  unite("name", first_name:last_name, sep=" ")
```

<br>

### [2.3]{style="color: lightgrey;"} Convert variables to correct data types

```{r class.source = "fold-show"}
# All character variables to factors
data <- data %>%
  mutate_if(sapply(data, is.character), as.factor)
```

<br>

### [2.4]{style="color: lightgrey;"} Create variable `coming_out_2` to easily explore subset

```{r class.source = "fold-show"}
data<- data %>% 
  mutate(coming_out_2 = ifelse(is.na(coming_out_nature_2), 0, 1) ,.after = gender)
```

<br>

------------------------------------------------------------------------

## [3]{style="color: steelblue;"} Data Visualization and Summary

------------------------------------------------------------------------

<br>

## [3.1]{style="color: lightgrey;"} Univariate Analysis 

<br>

### Categorical Variables

------------------------------------------------------------------------

## [3.1.1]{style="color: lightgrey;"} [Race]{style="color: steelblue;"}

```{r echo=TRUE, warning=TRUE, fig.align='center'}
pct_format <- scales::percent_format(accuracy = .1) #Used in the future bar plots

data %>%
  filter(race != "Unknown") %>%
  ggplot(aes(x = fct_infreq(race), fill = fct_infreq(race))) +
  geom_bar() +
  guides(fill = "none") +
  geom_text(
    aes(label = sprintf(
      "%d (%s)", ..count.., pct_format(..count.. / sum(..count..))
    )),
    stat = "count",
    nudge_y = 5,
    colour = "black",
    size = 4,
    fontface = "bold"
  ) +
  labs(title = "Figure 1.1", x = "", y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(size = 12, vjust = -1)) +
  scale_fill_manual(values = wes_palette("Moonrise3", 5, type = "continuous"))
```

```{r, fig.align='center'}
data %>%
  filter(!is.na(race)) %>%
  group_by(race) %>%
  rename(Race = race) %>%
  summarise(Frequency = n()) %>%
  mutate("Relative Frequency" = round(Frequency / sum(Frequency), 3)) %>%
  kable(caption = "TABLE 1.1: Race",
        format = "html",
        table.attr = "style='width:65%;'") %>%
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 18) %>%
  row_spec(0, bold = TRUE)
```


```{r}
# Create function to calculate return # of NAs in a variable
NA_calc <- function(x) {
  a <- sum(is.na(x))
  print(paste("Missing Values (NAs):" , a))
}
NA_calc(data$race)
```

<br>

------------------------------------------------------------------------

## [3.1.2]{style="color: lightgrey;"} [Gender]{style="color: steelblue;"}

```{r echo=TRUE, fig.align='center'}
data %>%
  filter(!is.na(gender)) %>%
  ggplot(aes(x = fct_infreq(gender), fill = fct_infreq(gender))) +
  geom_bar() +
  guides(fill = "none") +
  geom_text(
    aes(label = sprintf(
      "%d (%s)", ..count.., pct_format(..count.. / sum(..count..))
    )),
    stat = "count",
    nudge_y = 5,
    colour = "black",
    size = 3.5,
    fontface = "bold"
  ) +
  labs(title = "Figure 1.2", x = "", y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(
    size = 11,
    angle = 25,
    hjust = 1
  )) +
  scale_fill_manual(values = wes_palette("Moonrise3", 10, type = "continuous"))
```

```{r fig.align='center'}
data %>%
  filter(!is.na(gender)) %>%
  group_by(gender) %>%
  rename(Gender = gender) %>%
  summarise(Frequency = n()) %>%
  mutate("Relative Frequency" = round(Frequency / sum(Frequency), 3)) %>%
  kable(caption = "TABLE 1.2: Gender",
        format = "html",
        table.attr = "style='width:65%;'") %>%
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 18) %>%
  row_spec(0, bold = TRUE)
```

```{r fig.align='center'}
NA_calc(data$gender)
```

<br>

------------------------------------------------------------------------

## [3.1.3]{style="color: lightgrey;"} [Sexuality]{style="color: steelblue;"}

```{r message=FALSE, warning=FALSE, fig.align='center'}
#The value "Unspecified non heterosexual" fits poorly, so I have revalued it to "Non heterosexual".
data %>%
  filter(!is.na(sexuality)) %>%
  mutate(sexuality = fct_recode(sexuality, "Non heterosexual" = "Unspecified non heterosexual")) %>%
  ggplot(aes(x = fct_infreq(sexuality), fill = fct_infreq(sexuality))) +
  geom_bar() +
  guides(fill = "none") +
  geom_text(
    aes(label = sprintf(
      "%d (%s)", ..count.., pct_format(..count.. / sum(..count..))
    )),
    stat = "count",
    nudge_y = 5,
    colour = "black",
    size = 3.5,
    fontface = "bold"
  ) +
  labs(title = "Figure 1.3", x = "", y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(
    size = 12,
    angle = 35,
    hjust = 1.0
  )) +
  scale_fill_manual(values = wes_palette("Moonrise3", 9, type = "continuous"))
```

```{r fig.align='center'}
data %>%
  filter(!is.na(sexuality)) %>%
  group_by(sexuality) %>%
  mutate(sexuality = fct_recode(sexuality, "Non heterosexual" = "Unspecified non heterosexual")) %>%
  rename(Sexuality = sexuality) %>%
  summarise(Frequency = n()) %>%
  mutate("Relative Frequency" = round(Frequency / sum(Frequency), 3)) %>%
  kable(caption = "TABLE 1.3: Sexuality",
        format = "html",
        table.attr = "style='width:60%;'") %>%
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 18) %>%
  row_spec(0, bold = TRUE)
```

```{r fig.align='center'}
NA_calc(data$sexuality)
```

<br>

------------------------------------------------------------------------

## [3.1.2]{style="color: lightgrey;"} [In the closet?]{style="color: steelblue;"}

```{r message=FALSE, warning=FALSE, fig.align='center'}
data %>%
  filter(!is.na(closeted)) %>%
  ggplot(aes(x = closeted, fill = closeted)) +
  geom_bar() +
  guides(fill = "none") +
  geom_text(
    aes(label = sprintf(
      "%d (%s)", ..count.., pct_format(..count.. / sum(..count..))
    )),
    stat = "count",
    nudge_y = 5,
    colour = "black",
    size = 3.5,
    fontface = "bold"
  ) +
  labs(title = "Figure 1.4", x = "", y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(size=12, angle = 35, hjust = 1)) +
  scale_fill_manual(values = c("#85D4E3","LightBlue", "Linen", "#F4B5BD", "MistyRose"))
```

```{r fig.align='center'}
data %>%
  filter(!is.na(closeted)) %>%
  group_by(closeted) %>%
  rename("Closeted?" = closeted) %>%
  summarise(Frequency = n()) %>%
  mutate("Relative Frequency" = round(Frequency/sum(Frequency), 3)) %>%
  kable(caption = "TABLE 1.4: Closeted before coming out", 
        format = "html", 
        table.attr = "style='width:65%;'") %>% 
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 18) %>%
  row_spec(0,bold=TRUE)
```

```{r fig.align='center'}
NA_calc(data$closeted)
```

<br>

------------------------------------------------------------------------

## [3.1.5]{style="color: lightgrey;"} [Coming Out Medium]{style="color: steelblue;"}

```{r fig.align='center'}
data %>%
  filter(!is.na(medium)) %>%
  ggplot(aes(x = fct_infreq(medium), fill = fct_infreq(medium))) +
  geom_bar() +
  guides(fill = "none") +
  geom_text(
    aes(label = sprintf(
      "%d (%s)", ..count.., pct_format(..count.. / sum(..count..))
    )),
    stat = "count",
    nudge_y = 5,
    colour = "black",
    size = 3.5,
    fontface = "bold"
  ) +
  labs(title = "Figure 1.5", x = "", y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(size=11, angle=35, hjust = 1)) +
  scale_fill_manual(values = wes_palette("Moonrise3", 6, type = "continuous"))
```

```{r fig.align='center'}
data %>%
  group_by(medium) %>%
  filter(!is.na(medium)) %>%
  rename(Medium = medium) %>%
  summarise(Frequency = n()) %>%
  mutate("Relative Frequency" = round(Frequency/sum(Frequency), 3)) %>%
  kable(caption = "TABLE 1.5: Medium of coming out",
        format = "html", 
        table.attr = "style='width:65%;'") %>% 
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 18) %>%
  row_spec(0,bold=TRUE)
```

```{r fig.align='center'}
NA_calc(data$medium)
```

<br>

------------------------------------------------------------------------

## [3.1.6]{style="color: lightgrey;"} [Who Initiated Coming Out?]{style="color: steelblue;"}

```{r fig.width= 4, fig.align='center'}
data %>%
  filter(!is.na(initiation)) %>%
  ggplot(aes(x = fct_infreq(initiation), fill = fct_infreq(initiation))) +
  geom_bar() +
  guides(fill = "none") +
  geom_text(
    aes(label = sprintf(
      "%d (%s)", ..count.., pct_format(..count.. / sum(..count..))
    )),
    stat = "count",
    nudge_y = 5,
    colour = "black",
    size = 4,
    fontface = "bold"
  ) +
  labs(title = "Figure 1.6: Initiation", x = "", y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(size=12)) +
  scale_fill_manual(values = wes_palette("Moonrise3", 2, type = "continuous"))
```

```{r fig.align='center'}
data %>%
  group_by(initiation) %>%
  filter(!is.na(initiation)) %>%
  rename(Initiation = initiation) %>%
  summarise(Frequency = n()) %>%
  mutate("Relative Frequency" = round(Frequency/sum(Frequency), 3)) %>%
  kable(caption = "TABLE 1.6: Who initiated coming out",
        format = "html", table.attr = "style='width:65%;'") %>% 
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 18) %>%
  row_spec(0,bold=TRUE)
```

```{r fig.align='center'}
NA_calc(data$initiation)
```

<br>

------------------------------------------------------------------------

## [3.1.7]{style="color: lightgrey;"} [Who Disclosed?]{style="color: steelblue;"}

```{r fig.width= 4, fig.align='center'}
data %>%
  filter(!is.na(disclosure)) %>%
  ggplot(aes(x = fct_infreq(disclosure), fill = fct_infreq(disclosure))) +
  geom_bar() +
  guides(fill = "none") +
  geom_text(
    aes(label = sprintf(
      "%d (%s)", ..count.., pct_format(..count.. / sum(..count..))
    )),
    stat = "count",
    nudge_y = 5,
    colour = "black",
    size = 4,
    fontface = "bold"
  ) +
  labs(title = "Figure 1.7: Disclosure", x = "", y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(size=12)) +
  scale_fill_manual(values = wes_palette("Moonrise3", 2, type = "continuous"))
```

```{r fig.align='center'}
data %>%
  group_by(disclosure) %>%
  filter(!is.na(disclosure)) %>%
  rename(Disclosure = disclosure) %>%
  summarise(Frequency = n()) %>%
  mutate("Relative Frequency" = round(Frequency/sum(Frequency), 3)) %>%
  kable(caption = "TABLE 1.7: Who disclosed", format = "html", table.attr = "style='width:65%;'") %>% 
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 18) %>%
  row_spec(0,bold=TRUE)
```

```{r fig.align='center'}
NA_calc(data$disclosure)
```

<br>

------------------------------------------------------------------------

## [3.1.8]{style="color: lightgrey;"} [Had Second Coming Out?]{style="color: steelblue;"}

```{r fig.width= 4, fig.align='center'}
data %>%
  filter(!is.na(coming_out_2)) %>%
  mutate(coming_out_2 = as.factor(coming_out_2)) %>%
  mutate(coming_out_2 = if_else(coming_out_2 == "1", "Yes", "No")) %>%
  ggplot(aes(x = fct_infreq(coming_out_2), fill = fct_infreq(coming_out_2))) +
  geom_bar() +
  guides(fill = "none") +
  geom_text(
    aes(label = sprintf(
      "%d (%s)", ..count.., pct_format(..count.. / sum(..count..))
    )),
    stat = "count",
    nudge_y = 5,
    colour = "black",
    size = 4.5,
    fontface = "bold"
  ) +
  labs(title = "Figure 1.8", x = "", y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(size=12)) +
  scale_fill_manual(values = wes_palette("Moonrise3", 2, type = "continuous"))
```

```{r fig.align='center'}
data %>%
  group_by(coming_out_2) %>%
  filter(!is.na(coming_out_2)) %>%
  mutate(coming_out_2 = as.factor(coming_out_2)) %>%
  mutate(coming_out_2 = if_else(coming_out_2 == "1", "Yes", "No")) %>%
  rename("Had 2nd Coming Out" = coming_out_2) %>%
  summarise(Frequency = n()) %>%
  mutate("Relative Frequency" = round(Frequency/sum(Frequency), 2)) %>%
  kable(caption = "TABLE 1.8: Second coming out events", format = "html", table.attr = "style='width:65%;'") %>%
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 18) %>%
  row_spec(0,bold=TRUE)
```

```{r fig.align='center'}
NA_calc(data$coming_out_2)
```

<br>

------------------------------------------------------------------------

## [3.1.9]{style="color: lightgrey;"} [Second Coming Out Nature]{style="color: steelblue;"}

```{r fig.width= 4, fig.align='center'}
data %>%
  filter(coming_out_2 == 1, 
         !is.na(coming_out_nature_2)) %>%
  ggplot(aes(x = fct_infreq(coming_out_nature_2), fill = fct_infreq(coming_out_nature_2))) +
  geom_bar() +
  guides(fill = "none") +
  geom_text(
    aes(label = sprintf(
      "%d (%s)", ..count.., pct_format(..count.. / sum(..count..))
    )),
    stat = "count",
    nudge_y = 1,
    colour = "black",
    size = 4.5,
    fontface = "bold"
  ) +
  labs(title = "Figure 1.9", x = "", y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(size=12)) +
  scale_fill_manual(values = wes_palette("Moonrise3", 2, type = "continuous"))
```

```{r fig.align='center'}
data %>%
  group_by(coming_out_nature_2) %>%
  filter(coming_out_2 == 1,
         !is.na(coming_out_nature_2)) %>%
  rename("Nature" = coming_out_nature_2) %>%
  summarise(Frequency = n()) %>%
  mutate("Relative Frequency" = round(Frequency/sum(Frequency), 2)) %>%
  kable(caption = "TABLE 1.9: Nature of second coming out", format = "html", table.attr = "style='width:65%;'") %>%
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 18) %>%
  row_spec(0,bold=TRUE)
```

```{r fig.align='center'}
subset <- data %>%
  filter(coming_out_2 == 1)
NA_calc(subset$coming_out_nature_2)
```

<br>

------------------------------------------------------------------------

## [3.1.10]{style="color: lightgrey;"} [Second Coming Out Sexuality]{style="color: steelblue;"}

```{r fig.align='center'}
data %>%
  filter(coming_out_2 == 1, 
         !is.na(sexuality_2)) %>%
  mutate(sexuality_2 = fct_recode(sexuality_2,"Non heterosexual"= "Unspecified non heterosexual")) %>%
  ggplot(aes(x = fct_infreq(sexuality_2), fill = fct_infreq(sexuality_2))) +
  geom_bar() +
  guides(fill = "none") +
  geom_text(
    aes(label = sprintf(
      "%d (%s)", ..count.., pct_format(..count.. / sum(..count..))
    )),
    stat = "count",
    nudge_y = .65,
    colour = "black",
    size = 3.45,
    fontface = "bold"
  ) +
  labs(title = "Figure 1.10", x = "", y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 14,
                                  face = "bold")) +
  theme(axis.text.x = element_text(size=12, angle = 45, hjust = 1)) +
  scale_fill_manual(values = wes_palette("Moonrise3", 10, type = "continuous"))
```

```{r fig.align='center'}
data %>%
  mutate(sexuality_2 = fct_recode(sexuality_2, "Non heterosexual"= "Unspecified non heterosexual",
                                  "Unspecified" = "Unspecified ")) %>%
  group_by(sexuality_2) %>%
  filter(coming_out_2 == 1,
         !is.na(sexuality_2)) %>%
  rename("Sexuality" = sexuality_2) %>%
  summarise(Frequency = n()) %>%
  mutate("Relative Frequency" = round(Frequency/sum(Frequency), 2)) %>%
  kable(caption = "TABLE 1.10: Sexuality at second coming out", format = "html", table.attr = "style='width:75%;'") %>%
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 18) %>%
  row_spec(0,bold=TRUE)
```

```{r fig.align='center'}
NA_calc(subset$sexuality_2)
```

<br>


## [3.2.1]{style="color: lightgrey;"} [Current Age]{style="color: steelblue;"}

<br>

### - Current ages in 2022 based on birth year. For simplicity, I applied a filter to include only those under 100 years old

```{r echo=TRUE, message=FALSE, warning=FALSE, fig.align='center'}
p1 <- data %>%
  filter(!is.na(birth_year)) %>%
  mutate(current_age = 2022 - birth_year) %>%
  filter(current_age < 100) %>%
  ggplot(aes(x = current_age)) +
  geom_histogram(
    fill = "#85D4E3",
    colour = 1,
    binwidth = 5,
    size = .25
  ) +
  guides(fill = "none", colour = "none") +
  labs(title = "Figure 1.12",
       x = "Age",
       y = "Count") +
  coord_cartesian(xlim = c(10, 100), ylim = c(0, 40)) +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 20,
                                  face = "bold"))

p2 <- data %>%
  filter(!is.na(birth_year)) %>%
  mutate(current_age = 2022 - birth_year) %>%
  filter(current_age < 100) %>%
  ggplot(aes(x = current_age, y = ..density..)) +
  geom_density(lwd = .75, fill = "lightgray") +
  guides(fill = "none", colour = "none") +
  labs(x = "Age",
       y = "Density") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 20,
                                  face = "bold")) +
  xlim(0, 100) +
  geom_vline(
    aes(xintercept = median(current_age)),
    color = "red",
    size = 0.75,
    linetype = "longdash"
  ) +
  geom_text(aes(
    median(current_age),
    y = 0.03,
    label = paste("median =", median(current_age)),
    hjust = -.3,
  ),
  size = 5.9,
  face = "plain")

p1 + p2
```

```{r echo=TRUE, message=FALSE, warning=FALSE, fig.height= 3, fig.align='center'}
is.outlier <- function(x) {
  return(x  < quantile(x, 0.25) - 1.5 * IQR(x) |
           x > quantile(x, 0.75) + 1.5 * IQR(x))
}

data %>%
  filter(!is.na(birth_year)) %>%
  mutate(current_age = 2022 - birth_year) %>%
  mutate(Outlier = ifelse(is.outlier(current_age), current_age, "")) %>%
  ggplot(aes(x = current_age, y = "")) +
  geom_boxplot(
    fill = "lightgray",
    outlier.shape = 5,
    outlier.color = "red",
    outlier.size = 4
  ) +
  labs(title = "Boxplot of Current Age",
       x = "Age",
       y = "") +
  theme_classic() +
  theme(axis.ticks.y = element_blank(),
        axis.text.y  = element_blank()) +
  theme(plot.title = element_text(size = 14,
                                  face = "bold")) +
  geom_text_repel(aes(label = ifelse(duplicated(Outlier), "", Outlier))) +
  annotate("text", x = 41 + 5, y = 1.5, label = paste("median = 41"), fontface = 2)
```

```{r, fig.align='center'}
data %>%
  filter(!is.na(birth_year)) %>%
  mutate(current_age = 2022 - birth_year) %>%
  summarise(Mean =  round(mean(current_age),1),
            SD =  round(sd(current_age),1),
            Median = median(current_age),
            Min = min(current_age),
            Max = max(current_age),
            NAs = sum(is.na(age))
            ) %>%
  kable(caption = "TABLE 1.12: Summary of Current Ages", format = "html", table.attr = "style='width:40%;'") %>% 
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 20) %>%
  row_spec(0,bold=TRUE)
```

<br>

------------------------------------------------------------------------

## [3.2.2]{style="color: lightgrey;"} [Coming Out Year]{style="color: steelblue;"}

```{r echo=TRUE, message=FALSE, warning=FALSE, fig.align='center'}
p1 <- data %>%
  filter(!is.na(coming_out_year), 
         coming_out_year > 1940) %>%
  ggplot(aes(x = coming_out_year)) +
  geom_histogram(
    fill = "#85D4E3",
    colour = 1,
    binwidth = 2,
    size = .25
  ) +
  guides(fill = "none", colour = "none") +
  labs(title = "Figure 1.13",
       x = "Year",
       y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 20,
                                  face = "bold"))

p2 <- data %>%
  filter(!is.na(coming_out_year),
         coming_out_year > 1940) %>%
  ggplot(aes(x = coming_out_year, y = ..density..)) +
  geom_density(lwd = .75, fill = "lightgray") +
  guides(fill = "none", colour = "none") +
  labs(x = "Year",
       y = "Density") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 20,
                                  face = "bold")) +
  geom_vline(
    aes(xintercept = median(coming_out_year)),
    color = "red",
    size = 0.75,
    linetype = "longdash"
  ) +
  geom_text(aes(
    median(coming_out_year),
    y = 0.05,
    label = paste("median =", median(coming_out_year)),
    hjust = 1.2
  ),
  size = 5.9,
  face = "plain")

p1 + p2
```

```{r echo=TRUE, message=FALSE, warning=FALSE, fig.height= 3, fig.align='center'}
is.outlier <- function(x) {
  return(x  < quantile(x, 0.25) - 1.5 * IQR(x) |
           x > quantile(x, 0.75) + 1.5 * IQR(x))
}

data %>%
  filter(!is.na(coming_out_year)) %>%
  mutate(Outlier = ifelse(is.outlier(coming_out_year), coming_out_year, "")) %>%
  ggplot(aes(x = coming_out_year, y = "")) +
  geom_boxplot(
    fill = "lightgray",
    outlier.shape = 5,
    outlier.color = "red",
    outlier.size = 4
  ) +
  labs(title = "Boxplot of Coming Out Year",
       x = "Year",
       y = "") +
  theme_classic() +
  theme(axis.ticks.y = element_blank(),
        axis.text.y  = element_blank()) +
  theme(plot.title = element_text(size = 14,
                                  face = "bold")) +
  geom_text_repel(aes(label = ifelse(duplicated(Outlier), "", Outlier))) +
  annotate("text", x = median(data$coming_out_year, na.rm = T) -2, y = 1.5, label = paste("median = ", median(data$coming_out_year, na.rm = T)), fontface = 2)
```

```{r fig.align='center'}
data %>%
  filter(!is.na(coming_out_year)) %>%
  summarise(Mean =  round(mean(coming_out_year)),
            SD =  round(sd(coming_out_year)),
            Median = median(coming_out_year),
            Min = min(coming_out_year),
            Max = max(coming_out_year),
            NAs = sum(is.na(age))
            ) %>%
  kable(caption = "TABLE 1.13: Summary of Coming Out Years", format = "html", table.attr = "style='width:40%;'") %>% 
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 20) %>%
  row_spec(0,bold=TRUE)
```

<br>

------------------------------------------------------------------------

## [3.2.3]{style="color: lightgrey;"} [Age at Coming Out]{style="color: steelblue;"}

```{r echo=TRUE, message=FALSE, warning=FALSE, fig.align='center'}
p1 <- data %>% 
  filter(!is.na(age)) %>%
  ggplot(aes(x = age)) +
  geom_histogram(
    fill = "#85D4E3",
    colour = 1,
    binwidth = 2,
    size = .25
  ) +
  guides(fill = "none", colour = "none") +
  labs(title = "Figure 1.14",
       x = "Age",
       y = "Count") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 20,
                                  face = "bold"))

p2 <- data %>%
  filter(!is.na(age)) %>%
  ggplot(aes(x = age, y = ..density..)) +
  geom_density(lwd = .75, fill = "lightgray") +
  guides(fill = "none", colour = "none") +
  labs(x = "Age",
       y = "Density") +
  theme_classic() +
  theme(plot.title = element_text(color = "black",
                                  size = 20,
                                  face = "bold")) +
  geom_vline(
    aes(xintercept = median(age)),
    color = "red",
    size = 0.75,
    linetype = "longdash"
  ) +
  annotate("text",
           x = median(data$age, na.rm = T),
           y = 0.035,
           label = paste("median =", median(data$age, na.rm = T)),
           hjust = -.35,
           fontface = 2,
           size = 5.9)

p1 + p2
```

```{r echo=TRUE, message=FALSE, warning=FALSE, fig.height= 3, fig.align='center'}
is.outlier <- function(x) {
  return(x  < quantile(x, 0.25) - 1.5 * IQR(x) |
           x > quantile(x, 0.75) + 1.5 * IQR(x))
}

data %>%
  filter(!is.na(age)) %>%
  mutate(Outlier = ifelse(is.outlier(age), age, "")) %>%
  ggplot(aes(x = age, y = "")) +
  geom_boxplot(
    fill = "lightgray",
    outlier.shape = 5,
    outlier.color = "red",
    outlier.size = 4
  ) +
  labs(title = "Boxplot of Coming Out Age",
       x = "Age",
       y = "") +
  theme_classic() +
  theme(axis.ticks.y = element_blank(),
        axis.text.y  = element_blank()) +
  theme(plot.title = element_text(size = 14,
                                  face = "bold")) +
  geom_text_repel(aes(label = ifelse(duplicated(Outlier), "", Outlier))) +
  annotate("text", x = median(data$age, na.rm = T) + 10, y = 1.5, label = paste("median = ", median(data$age, na.rm = T)), fontface = 2)
```

```{r fig.align='center'}
data %>%
  filter(!is.na(age)) %>%
  summarise(Mean =  round(mean(age),1),
            SD =  round(sd(age),1),
            Median = median(age),
            Min = min(age),
            Max = max(age),
            NAs = sum(is.na(age))
            ) %>%
  kable(caption = "TABLE 1.14: Summary of Coming Out Age", format = "html", table.attr = "style='width:40%;'") %>% 
  kable_classic() %>%
  kable_styling(bootstrap_options = c("striped"), font = 20) %>%
  row_spec(0,bold=TRUE)
```

<br>

------------------------------------------------------------------------

## [3.2]{style="color: lightgrey;"} Multivariate Analysis

<br>

------------------------------------------------------------------------



<br>

<br>
